---
title: "EX2"
author: "Anits Sherin (21bcs065)"
date: "2024-01-22"
output: pdf_document
---
1. write the R/Y command to install a package
```{r}
install.packages("tidyverse")
```

2. load and use a package
```{r}
library(tidyverse)
```
3. unload a package
```{r}
detach
```

4. update a package
```{r}
install.packages("tidyverse", update = TRUE)
```
5. Remove an installed package from your computer
```{r}
remove.packages("package_name")
```
6. load the iris dataset and explore the following
a) display the structure of Iris dataset 
```{r}
data(iris)
str(iris)
```
b) display the column names
```{r}
data(iris)
column_names <- colnames(iris)
print(column_names)
```
c) find the data type / class of each feature or column.
```{r}
data(iris)
column_data_types <- sapply(iris, class)
print(column_data_types)
```
d) display first 10 samples/ row of the dataset.
```{r}
data(iris)
first_10_rows <- head(iris, 10)
print(first_10_rows)
```
e)display last 10 data of the feature Sepal.Length
```{r}
data(iris)
last_10_sepal_length <- tail(iris$Sepal.Length, 10)
print(last_10_sepal_length)
```
f) analyse and produce a summary of the Petal.Length
```{r}
data(iris)
summary(iris$Petal.Length)
```
g)find out the number of samples in each class of iris dataset
```{r}
data(iris)
class_counts <- table(iris$Species)
print(class_counts)
```
h) write your iris data as a 'myiris.csv' 
```{r}
data(iris)
write.csv(iris, file = "myiris.csv", row.names = FALSE)
```

7) load the inbuilt titanic dataset from kaggle and do the following.
```{r}
titanic <- read.csv("train.csv")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
