---
title: "ex1"
author: "Anits Sherin(21bcs065)"
date: "2024-01-08"
output: pdf_document
---
1. Generate 10 uniformly distributed numbers(0,1)
```{r}
uniform_numbers<-runif(10)
print(uniform_numbers)

```

2. Display them using plot.
```{r}
plot(uniform_numbers)
```
3. Generate 5 random integers 1:10 with and without replacment
```{r}
sample(1:10,5,replace=TRUE)
sample(1:10,5,replace=FALSE)

```
4. select 2 random months from a list of months. Combine 2 strings with comma separation.
```{r}
months<-month.name
random_months<-sample(months,size=2)
combined_months<-paste(random_months,collapse=",")
print(combined_months)
```
5. prefix and suffix word with A
```{r}
word<-"example"
prefixed_word<-paste("A",word,sep="")
suffixed_word<-paste(word,"A",SEP="")
print(prefixed_word)
print(suffixed_word)
```
6. Find number of characters in a string.
```{r}
my_string<-"this is a string"
num_chars<-nchar(my_string)
print(num_chars)`

```
7. Construct a vector of odd numbers 1 to 10 using seq()
```{r}
odd_numbers<-seq(from=1,to=10,by=2)
print(odd_numbers)

```
8.Find it's log to the base 10 and sine values.
```{r}
number<-15
log10value<-log10(number)
sin_value<-sin(number)
print(paste("log to the base 10:",log10value))
print(paste("sine value:",sin_value))
```
9. find sum, mean, median, length, variance, standard deviation, quantile.
```{r}
data<-c(4,8,15,16,23,43)
sum(data)
mean(data)
mean(data)
median(data)
length(data)
var(data)
quantile(data)

```
10. find summary on the same
```{r}
summary(data)

```
11. get today's date and time
```{r}
print(Sys.time())

```
12. find your age in days
```{r}
today_date<-Sys.Date()
bday<-as.Date("2003-06-01")
age<-as.numeric(today_date-bday)
print(age)

```
13. convert to lower and upper case
```{r}
x<-"hello world"
lower_text<-tolower(x)
upper_text<-toupper(x)
print(lower_text)
print(upper_text)

```
14. extract the last three characters of the string.
```{r}
string<-"hello world"
last_three<-substr(string,nchar(string)-2,nchar(string))
print(last_three)

```
15.sort the string in lexicographic order
```{r}
word<-c("a","n","i","t","s")
sorted<-sort(word)
print(sorted)
```
16.  display string that starts with A
```{r}
strings<-c("apple","Anits","Avocado")
startswithA<-grep("^A",strings,value=TRUE)
print(startswithA)
```
17. HOW MANY COMMON WORDS START WITH t
```{r}
common_words<-c("tent","text","anits")
t_words<-common_words[startsWith(common_words,"t")]

print(t_words)

```
18. how many common words end with a vowel
```{r}
common_words<-c("hello","apple","tree","mason")
vowel_words<-grep("[aeiou]$",tolower(common_words))
c<-length(vowel_words)
print(c)
```

19. Find all words containing at least one vowel and negate.
```{r}
words <- c("apple", "banana", "grape", "sky", "fly", "dry")
pattern <- "[aeiou]"
words_with_vowel <- grep(pattern, words, value = TRUE)
words_without_vowel <- setdiff(words, words_with_vowel)
print(words_without_vowel)
```
20.find all words consisting only of consonants.
```{r}
words <- c("apple", "banana", "grape", "sky", "fly", "dry")
pattern <- "^[^aeiou]+$"
consonant_words <- grep(pattern, words, value = TRUE)
print(consonant_words)

```





## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
